Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-16 paper.tex
fix imports in code sample and explain feature selection method

As an example, the following snippet illustrates how to create a complex worflow
computing both linear PCA and kernel PCA components on \texttt{X\_train}
(through a \texttt{FeatureUnion}), selecting the 100 best of those features and
then feeding them to an $\ell_2$-regularized logistic regression model:
\begin{pythoncode}
from sklearn.pipeline import Pipeline
from sklearn.decomposition import PCA, KernelPCA
from sklearn.feature_selection import SelectKBest

>>>>

As an example, the following snippet illustrates how to create a complex worflow
computing both linear PCA and kernel PCA components on \texttt{X\_train}
(through a \texttt{FeatureUnion}),
selecting the 100 best of those features according to an ANOVA test
and then feeding them to an $\ell_2$-regularized logistic regression model:
\begin{pythoncode}
from sklearn.pipeline import FeatureUnion, Pipeline
from sklearn.decomposition import PCA, KernelPCA
from sklearn.feature_selection import SelectKBest
from sklearn.linear_model import LogisticRegression
